Are rankings of financial analysts useful to investors?

### 2015-03-17 doc/paper/paper-knitr-APS.tex
working paper but only one choice for type (either 'all' or 'same')
paper with table side-by-side all and same set of stocks

\usepackage{alltt}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
%\onehalfspacing
\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%) & Median (in \%) &Std.dev\\
\midrule
  \multicolumn{4}{l}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.577 & 16.861 & 0.119 \\ 
  \naive{} & 18.615 & 16.866 & 0.120 \\ 
  \default{} & 21.729 & 20.478 & 0.102 \\

@@

  \begin{tabularx}{\linewidth}{r*{4}{Y}}
  \midrule
  \multicolumn{4}{l}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 14.893 & 13.407 & 0.102 \\ 
  \naive{} & 14.895 & 13.393 & 0.103 \\ 
  \default{} & 19.394 & 18.602 & 0.088 \\

  \end{tabularx}
  \begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 15.719 & 14.303 & 0.098 \\ 
  \naive{} & 15.738 & 14.304 & 0.098 \\ 
  \default{} & 18.836 & 17.795 & 0.086 \\

@@

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 &  219 &  219 &  144 \\ 
  2000 &  295 &  295 &  211 \\ 
  2001 &  341 &  341 &  257 \\ 
  2002 &  374 &  374 &  299 \\ 
  2003 &  390 &  390 &  311 \\ 
  2004 &  399 &  399 &  331 \\ 
  2005 &  414 &  414 &  343 \\ 
  2006 &  421 &  421 &  344 \\ 
  2007 &  426 &  426 &  357 \\ 
  2008 &  420 &  420 &  339 \\ 
  2009 &  365 &  365 &  300 \\ 
   \midrule 
Total &  442 &  442 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   73 &   73 &   44 \\ 
  2000 &  257 &  257 &  185 \\ 
  2001 &  310 &  310 &  247 \\ 
  2002 &  362 &  362 &  288 \\ 
  2003 &  374 &  374 &  307 \\ 
  2004 &  385 &  385 &  318 \\ 
  2005 &  401 &  401 &  337 \\ 
  2006 &  415 &  415 &  343 \\ 
  2007 &  421 &  421 &  352 \\ 
  2008 &  422 &  422 &  349 \\ 
  2009 &  405 &  405 &  321 \\ 
   \midrule 
Total &  442 &  442 &  376 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   73 &   73 &   54 \\ 
  2000 &  257 &  257 &  205 \\ 
  2001 &  314 &  314 &  264 \\ 
  2002 &  368 &  368 &  308 \\ 
  2003 &  383 &  383 &  326 \\ 
  2004 &  396 &  396 &  339 \\ 
  2005 &  414 &  414 &  357 \\ 
  2006 &  429 &  429 &  365 \\ 
  2007 &  438 &  438 &  371 \\ 
  2008 &  440 &  440 &  375 \\ 
  2009 &  442 &  442 &  378 \\ 
   \midrule 
Total &  442 &  442 &  378 \\

@@

%'   \begin{table}[hp]
%'   \caption{Descriptive statistics of views: \tr{}}
%'   \label{tab:view-stat}
%'   \small\addtolength{\tabcolsep}{-2pt}
%'   
%' \ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) for the \tr{} (\ref{q:true}) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
%'   
%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'     \toprule
%' Year &Stocks& Mean & Median &Std.dev\\
%' \midrule
%' <<desc-nr.views,echo=F,results='asis'>>=
%' 
%' print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
%' @
%'   \midrule
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-r.views,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' #cat(rep('&',ncol(results.final)),'\\\\')
%' print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
%' @
%'   \end{tabularx}
%'   
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-eps.views,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
%' @
%' \bottomrule
%'   \end{tabularx}
%' \end{table}
%' 
%' 
%' \begin{table}[hp]
%'   \caption{Descriptive statistics of views: \naive{}}
%'   \label{tab:view-stat-naive}
%'   \small\addtolength{\tabcolsep}{-2pt}
%'   
%' \ This table shows descriptive statistics of views (expected returns) for the \naive{} (\ref{q:naive}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
%'   
%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'     \toprule
%' Year &Stocks& Mean & Median &Std.dev\\
%' \midrule
%' <<desc-nr.views-naive,echo=F,results='asis'>>=
%' 
%' print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
%' @
%'   \midrule
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-r.views-naive,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' #cat(rep('&',ncol(results.final)),'\\\\')
%' print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
%' @
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-eps.views-naive,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
%' @
%' \bottomrule
%'   \end{tabularx}
%' \end{table}
%' 
%' \begin{table}[hp]
%'   \caption{Descriptive statistics of views: \default{}}
%'   \label{tab:view-stat-default}
%'   \small\addtolength{\tabcolsep}{-2pt}
%'   
%' \ This table shows descriptive statistics of views (expected returns) for the \default{} (\ref{q:default}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
%'   
%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'     \toprule
%' Year &Stocks& Mean & Median &Std.dev\\
%' \midrule
%' <<desc-nr.views-default,echo=F,results='asis'>>=
%' 
%' print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n','\\midrule \n')))
%' @
%'   \midrule
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-r.views-default,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' #cat(rep('&',ncol(results.final)),'\\\\')
%' print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
%' @
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-eps.views-default,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
%' @
%' \bottomrule
%'   \end{tabularx}
%' \end{table}

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
 \textit{CONS} & 1.893 & 15.147 & 0.125 &  291 & 0.291 \\ 
  \textit{TP} & 5.116 & 14.593 & 0.351 &  291 & 0.314 \\ 
  \textit{EPS} & 1.860 & 15.172 & 0.123 &  209 & 0.503 \\ 
   \midrule

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.126 & 15.947 & 0.008 &  284 & 0.256 \\ 
  \textit{TP} & 0.281 & 15.661 & 0.018 &  284 & 0.264 \\ 
  \textit{EPS} & -0.318 & 16.094 & -0.020 &  206 & 0.409 \\ 
   \midrule

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & -0.069 & 15.817 & -0.004 &  290 & 0.188 \\ 
  \textit{TP} & -0.005 & 15.633 & -0.000 &  290 & 0.192 \\ 
  \textit{EPS} & 0.441 & 15.673 & 0.028 &  250 & 0.198 \\

>>>>

\usepackage{alltt}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
%\usepackage{floatpag}
%\onehalfspacing
\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.577 & 18.947 & 16.861 & 17.156 & 0.119 & 0.119 \\ 
  \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
  \default{} & 21.729 & 22.216 & 20.478 & 20.715 & 0.102 & 0.101 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \midrule
  \multicolumn{7}{c}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 15.719 & 16.071 & 14.303 & 14.525 & 0.098 & 0.098 \\ 
  \naive{} & 15.738 & 16.098 & 14.304 & 14.528 & 0.098 & 0.098 \\ 
  \default{} & 18.836 & 19.352 & 17.795 & 18.195 & 0.086 & 0.084 \\

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{c}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 14.893 & 14.964 & 13.407 & 13.449 & 0.102 & 0.103 \\ 
  \naive{} & 14.895 & 14.967 & 13.393 & 13.432 & 0.103 & 0.103 \\ 
  \default{} & 19.394 & 19.511 & 18.602 & 18.756 & 0.088 & 0.089 \\

@@

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C).

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
&all&same&all&same&all&same\\
  \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 &  219 &  202 &  219 &  202 &  144 &  145 \\ 
  2000 &  295 &  269 &  295 &  269 &  211 &  211 \\ 
  2001 &  341 &  306 &  341 &  306 &  257 &  257 \\ 
  2002 &  374 &  333 &  374 &  333 &  299 &  299 \\ 
  2003 &  390 &  346 &  390 &  346 &  311 &  311 \\ 
  2004 &  399 &  351 &  399 &  351 &  331 &  331 \\ 
  2005 &  414 &  358 &  414 &  358 &  343 &  343 \\ 
  2006 &  421 &  360 &  421 &  360 &  344 &  344 \\ 
  2007 &  426 &  364 &  426 &  364 &  357 &  357 \\ 
  2008 &  420 &  360 &  420 &  360 &  339 &  339 \\ 
  2009 &  365 &  323 &  365 &  323 &  300 &  300 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  376 &  376 \\

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   73 &   69 &   73 &   69 &   44 &   44 \\ 
  2000 &  257 &  235 &  257 &  235 &  185 &  186 \\ 
  2001 &  310 &  281 &  310 &  281 &  247 &  247 \\ 
  2002 &  362 &  323 &  362 &  323 &  288 &  288 \\ 
  2003 &  374 &  334 &  374 &  334 &  307 &  307 \\ 
  2004 &  385 &  341 &  385 &  341 &  318 &  318 \\ 
  2005 &  401 &  352 &  401 &  352 &  337 &  337 \\ 
  2006 &  415 &  358 &  415 &  358 &  343 &  343 \\ 
  2007 &  421 &  361 &  421 &  361 &  352 &  352 \\ 
  2008 &  422 &  360 &  422 &  360 &  349 &  349 \\ 
  2009 &  405 &  351 &  405 &  351 &  321 &  321 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  376 &  376 \\

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   73 &   69 &   73 &   69 &   54 &   54 \\ 
  2000 &  257 &  235 &  257 &  235 &  205 &  205 \\ 
  2001 &  314 &  284 &  314 &  284 &  264 &  264 \\ 
  2002 &  368 &  327 &  368 &  327 &  308 &  308 \\ 
  2003 &  383 &  341 &  383 &  341 &  326 &  326 \\ 
  2004 &  396 &  350 &  396 &  350 &  339 &  339 \\ 
  2005 &  414 &  364 &  414 &  364 &  357 &  357 \\ 
  2006 &  429 &  370 &  429 &  370 &  365 &  365 \\ 
  2007 &  438 &  374 &  438 &  374 &  371 &  371 \\ 
  2008 &  440 &  376 &  440 &  376 &  375 &  375 \\ 
  2009 &  442 &  378 &  442 &  378 &  378 &  378 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  378 &  378 \\

@@

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
  &all&same&all&same&all&same&all&same&all&same \\

 \textit{CONS} & 1.893 & 2.247 & 15.147 & 15.032 & 0.125 & 0.149 &  291 &  257 & 0.291 & 0.277 \\ 
  \textit{TP} & 5.116 & 5.400 & 14.593 & 14.552 & 0.351 & 0.371 &  291 &  257 & 0.314 & 0.298 \\ 
  \textit{EPS} & 1.860 & 1.957 & 15.172 & 15.145 & 0.123 & 0.129 &  209 &  209 & 0.503 & 0.501 \\ 
   \midrule

\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.126 & 0.449 & 15.947 & 15.993 & 0.008 & 0.028 &  284 &  252 & 0.256 & 0.250 \\ 
  \textit{TP} & 0.281 & 0.622 & 15.661 & 15.682 & 0.018 & 0.040 &  284 &  252 & 0.264 & 0.256 \\ 
  \textit{EPS} & -0.318 & -0.361 & 16.094 & 16.100 & -0.020 & -0.022 &  206 &  206 & 0.409 & 0.408 \\ 
   \midrule

\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & -0.069 & 0.413 & 15.817 & 15.873 & -0.004 & 0.026 &  290 &  257 & 0.188 & 0.185 \\ 
  \textit{TP} & -0.005 & 0.441 & 15.633 & 15.658 & -0.000 & 0.028 &  290 &  257 & 0.192 & 0.189 \\ 
  \textit{EPS} & 0.441 & 0.441 & 15.673 & 15.702 & 0.028 & 0.028 &  250 &  250 & 0.198 & 0.198 \\
